Approximate \revised{Translational} Building Blocks for Image Parsing and Synthesis

### 2014-11-05 Paper/paper.tex
paper update

\markboth{xxx et al.}{Approximate Building Blocks for Image Parsing and Synthesis}

\title{Approximate Building Blocks for Image Parsing and Synthesis} % title

@@

\acmformat{xxx and xxx, 2015. Approximate Building Blocks for Image Parsing and Synthesis.  {ACM Trans. Graph.} xx, xx, Article xx (xx 2015), xx pages.\newline  DOI $=$
xxxx}

@@

\begin{abstract} 
In this paper, we introduce the concept of approximate building blocks for fully-automatic image parsing. We consider translational repetitive elements in images and characterize building blocks as maximal, coherently transformed regions that are instantiated frequently. We develop an algorithm for constructing approximate building blocks from noisy and ambiguous image features, based on a spectral embedding of co-occurrence patterns. We evaluate our method on a large benchmark data set and obtain clear improvements over state-of-the-art methods. We apply our image parsing method to texture synthesis, where we improve results by learning patterns of nearby landmarks induced by the building blocks, which also leads to quality improvements over previous work.
\end{abstract}

@@

Our paper addresses the problem of finding building blocks in image data using a fully unsupervised algorithm, i.e., it does not require any prior training data or user intervention. This restriction is very useful when we want to utilize the building block decompositions as structural side information for other tasks. We explore this exemplarily for image synthesis from example images.

@@

We replace structural priors by the assumption of coherently mapped building blocks, which are related by a common transformation and residual distortions. We discover such structures by relating co-occurance maps of images features using a spectral embedding, which draws its robustness out of the ability to use the whole 4D matching information in a single optimization for discovering coherently mapped pieces. We evaluate our method on a large benchmark data set of facade images. In comparison to previous methods, both with \cite{Wu2010DL} and without structural priors \cite{LIPMANsig2010,Liu2013GRASP}, we obtain a significant improvement.

To demonstrate the utility of building block information to generative tasks in computer graphics, we apply our method to guide image synthesis. Traditional texture synthesis methods~\cite{EfrosL99NP,Wei2000FT,Kwatra2003Graphcut,Kwatra2005TO} rely on a local, Markovian structure model that is oblivious to higher level constraints and therefore cannot produce images that are meaningfully structured on a coarser scale without human annotation~\cite{Hertzmann2001IA}. We use building blocks as landmarks and learn their relative placement and include this information into the image synthesis model. This leads to improvements over earlier Markovian models \cite{Kwatra2005TO}. We also compare to the latest state-of-the-art method based on statistical priors of image offsets~\cite{He2012PO}. Our method yields comparable or better results, and provides an additional semantic annotation layer, which can used for user interaction in constrained image synthesis.

In summary, the main contribution of this paper is a new approach for discovering \emph{approximate building blocks} in unreliable data. We develop the idea in the context of an automatic image parsing technique that discovers translational building blocks, and outperforms previous methods in this task. We demonstrate the utility of the discovered building blocks and their geometric relations by applying it to image synthesis, where we can get improvements over unguided methods without sacrificing the fully automatic mode of operation.

@@

\textbf{Texture synthesis} has received a lot of attention in computer graphics, see \cite{Wei2009STAR} for a comprehensive survey. In order to overcome the limitations of the Markov Random Field (MRF) model, various forms of guidance have been employed, for example, using an additional image layer with user annotations \cite{Hertzmann2001IA} or on-the-fly user interaction ~\cite{Barnes2009,Hu2013PPI}. Automating the creation of guidance map is still an on-going research topics, with some success in low level feature maps. For example, Lefebvre and Hoppe~\shortcite{Lefebvre2006ATS} use distance transforms on feature maps to guide the synthesis of high-quality textures with pronounced meso-structure. However, the feature transform cannot structure complex images beyond textures. Rosenberger et al.~\shortcite{Rosenberger2009LSS} extend the idea to irregular textures with non-stationary statistics, such as aged or weathered surfaces. Dishler et al.~\shortcite{Dischler2002} use ``texture particles'' as landmarks, similar to our guidance scheme; however, only textures (with some meso-structure) are synthesized due to limitations in the detection stage. Tiling grammars have been recently employed to guide the placement of discrete elements~\cite{Ma2011DET,Ma2013DET}, however our method handles image data, such as pixels color and class labels, rather than discrete elements. Our application is also related to image retargeting, recomposition and inpainting. Along this direction, various methods have been experimented to avoid local optimal solutions results from the MRFs model. For example, \cite{Simakov2008SV} uses bidirectional matching and a gradual resizing procedure for retain the image structure in retargeting (especially for image shrinking); \cite{Pritch09ICCV,He2012PO} studied pixel offset, and use graph cut to find the optimal pixel assignment for the output image that produces a smooth offset field. Nonetheless, these methods all operate on image pixels, hence can not eliminate structural artefacts. An exception is \cite{Wu2010SS}, which use deformable lattice to retain structure during image resizing. However their method is restricted to images has a global repetition (such as lattice), and is difficult to be used for recomposition. In this paper we will show using additional structure knowledge is able to improve the performance of the conventional pixel based MRF methods.

@@

\subsection{Dataset}
In order to prove our algorithm is able to identify meaningful building blocks, we conduct an evaluation on the fa{\c{c}}ade data set created by \cite{ZHANGsig13}. This data set contains 600 fa{\c{c}}ade images of various structures. For each image a box pattern has been interactive created by the authors, identifying repetitive elements such as windows or balconies. We use these labels as the ground truth to quantitatively evaluate our detection. We remove non-repetitive boxes from the data set (7285 boxes remain). We also test our algorithm on a collection of non-facade images. The results can be found in the supplementary materials.

@@

@@

\revised{
The key idea is to augment the conventional pixel based MRF models \cite{Pritch09ICCV} using an additional layer of building block information. Specifically, we propose two different types of building blocks constraints: First, as each pixel has a building block class label (zero for the background), so it should be distinguishable from pixels of different classes. Second, each pixel, except for the background, can be augmented by the local coordinate frame of its parent building block, so it can be distinguished from other pixels inside the same building block. Inspired by the success of pixel offset statistics \cite{He2012PO}, we use building blocks offset statistics to generate better candidate shifts for stitching.}

\revised{
The rest of this section explains how to apply these additional constraints for two specific applications: image targeting and interactive editing. Although in this paper we apply the constraints to synthesis methods that based on image stitching (\cite{Pritch09ICCV,He2012PO}), in principle they can be also applied to synthesis methods that use patch blending, such as \cite{Kwatra2005TO} and \cite{Simakov2008SV}. We choose to focus on the former methods because they perform better for synthesizing regular or semi-regular structures. Nonetheless results from \cite{Kwatra2005TO} and \cite{Simakov2008SV} will also be extensively discussed in the paper and in the supplementary materials.
}

@@

The goal of image retargeting is to synthesis new images by resizing. In \cite{Pritch09ICCV} and \cite{He2012PO} this is cast as a labeling problem, where each pixel in the synthesized image is assigned with a offset label that maps it back to the input image. Candidate labels $L$ can be generated by prescription \cite{Pritch09ICCV},  or by co-occurrence statistics \cite{He2012PO}. They are assigned to the synthesized image by minimizing the standard MRF energy function (Equation \ref{eq:GC}). Although these method are designed to find optimal labeling assignment, implausible stitches can still occur due to only pixel level energy is minimized (Figure \ref{fig:SynCompare}, see the bottom left and bottom middle pictures of each group).

\subsubsection{Building Blocks Constraints}

To overcome this problem, we incorporate building block constraints into the energy function. \revised{The idea is straight forward: as frequently appearing objects, building blocks should be prevented from mis-configuration and distortion.} Based on this idea, we redefine the smoothness term as the following:

\revised{
\begin{equation}
E_{s} = \omega_{1}E_{s}^{pixel} + \omega_{2}E_{s}^{class} + \omega_{3}E_{s}^{position}
\label{eq:EPixelSmooth}
\end{equation}
}

Here $E_{s}^{pixel}$ is the conventional pixel-based smoothness term as used by \cite{Pritch09ICCV} and \cite{He2012PO}. It penalizes two neighboring labels $a, b$ that creates a seam for adjacent pixels $x, x'$:
%
\begin{equation}
E_{s}^{pixel}(x, x', a, b) = |I(x + s_{a}) - I(x + s_{b})| + |I(x' + s_{a}) - I(x' + s_{b})|
\label{eq:ESmooth}
\end{equation}
%
In addition to it, we define two building block costs: the class smoothness cost $E_{s}^{class}$ and the position smoothness cost $E_{s}^{position}$. They are Potts models with different properties.

\revised{\textbf{Class smoothness term:} Let $l(x)$ be the building blocks class label for pixel $x$, the class smoothness term computes the hamming distance between class labels: $E_{s}^{class} = l(x + s_{a}) \neq l(x + s_{b}) + l(x' + s_{a}) \neq l(x' + s_{b})$.} It penalizes falsely stitching together pixels from different building block classes \revised{so is able to reduce mis-configurations}.

\revised{\textbf{Position smoothness term:} Let $(r(x), c(x))$ be the relative row and column position for pixel $x$ in its parent building blocks's local frame. The position smoothness cost computes the Manhattan distance between the relative positions: $E_{s}^{position} = w(x)(|r(x + s_{a}) - r(x + s_{b})| + |c(x + s_{a}) - c(x + s_{b})|) + w(x')(|r(x' + s_{a}) - r(x' + s_{b})| + |c(x' + s_{a}) - c(x' + s_{b})|)$}. It penalizes internally mis-configured building blocks \revised{so is able to prevent distortions}. Notice this term is only activated for pixels that are assigned with the same class label, \revised{that is $w(x) = l(x + s_{a}) == l(x + s_{b})$. In the meantime $r(x)$ and $c(x)$ are normalized according to the size of the parent building block so $r(x) \in [0, 1]$ and $c(x) \in [0, 1]$}. In this way the position smoothness term has the class smoothness cost as the upper bound. Only in this way the sub-modular constraint for graph cut optimization \cite{BOYKOVpami2001} can be met.

@@

 \revised{\textbf{Weights:} Notice the three costs in Equation \ref{eq:ESmooth} share the same lower bound (zero) but different upper bounds: $sup E_{s}^{pixel} = 255 \times 2 = 500$, $sup E_{s}^{class} = 1 \times 2 = 2$, and $sup E_{s}^{position} = 1 \times 4 = 4$. This implies we should weight them carefully so none of them, especially $E_{s}^{pixel}$, becomes predominant. In practice we also observed that artifacts in the conventional MRF models are rarely created by large $E_{s}^{pixel}$, as large pixel costs are naturally removed by graph cut as obvious seams. In fact, these artifacts are often created by stitching together pixels of similar values, in which case $E_{s}^{pixel}$ is small. This leads to the conclusion that building blocks costs should give enough influence, but not overkill, the low pixel costs. In practice we find $\omega_{1} = 1, \omega_{2} = 10, \omega_{3} = 2$ works robustly across a wide range of images. Although they can be further tuned on a per image basis for better results, we fix them to these default values in the later user study for fair comparisons.}

\revised{Figure \ref{fig:IntermediumSyn} shows an example of how the building blocks costs improve the result. The conventional MRF based method \cite{Pritch09ICCV} creates the result in Figure \ref{fig:IntermediumSyn} b). While the stitching of the arches is clearly artificial to human, it is hard to be avoided if only pixel cost is considered. With the help of the building blocks costs we are able to reduce the artifacts to Figure \ref{fig:IntermediumSyn} c). The improvement is more obvious in the class label map, shown in the bottom row of the figure. Especially, the noisy yellow labels at the floor of b) is removed, which results in more plausible synthesis in c).}

\subsubsection{Building Blocks Based Offsets}
\revised{Another important factor for achieving high quality synthesis results is the input offset labels for graph cut optimization. These labels directly decide the complexity of the search space and whether the minimized energy leads to a visually plausible image. For image completion, regular sampled offsets can be too dense or too sparse for achieving high quality results, as observed by \cite{He2012PO}. This is also true for image regarting. For example, in Figure \ref{fig:IntermediumSyn} c) a window is squeezed at the center of the image, despite the use of building blocks constraints. This is due to the fact that offset labels are sampled using a grid generator that deviates from regularities in the facade. In summary, building blocks constraints are less useful if the search space does not accommodate a useful solution in the first place.}

\revised{To address this problem, we sample offset labels from building blocks offset statistics. In this way both the search space and the constraints are based on the knowledge of building blocks. This often leads to further improvement of the synthesis results, as shown in Figure \ref{fig:IntermediumSyn} d). Our sampling contains two main steps: It first computes predominant offsets between the same class of building blocks. These offsets are then used as generators to regularly generate input labels for graph cut. Specifically, it works as follows: A probability density map (PDF) is computed by accumulating votes of pairwise building blocks offsets. Only building blocks of the same class are considered in the voting. We then detect local peaks in the PDF using non-maximum suppression. These local peaks were used in previous works as offset labels for image completion, as described in \cite{He2012PO}. Differently, for our task of image retargeting a larger montage must be created to fully cover the synthesis domain. In theory this can be achieved by recursively sampling new peaks from the PDF. However the number of offsets will be increased by a power function and the search becomes infeasible in practice. To handle this problem, we find predominant offsets and use them as grid generators to efficiently create the montage: the first generator is the strongest peak in the PDF, and the second generator is the next strongest peak that satisfies a minimum angular distance to the first generator. The minimum angular (set to $\frac{\pi}{3}$) requirement de-correlates the two generators so the montage can be efficiently expanded as a 2-D grid in both horizontal and vertical directions. In the pursuit of higher variability in the result, additional generators can be combined with these two to create extra grids. For example, randomness in the synthesis results can be created using a near-regular grid. However, in practice we found a regular grid spanned by two predominate generators trades off well between stability and variability.}

\revised{Since we use grid based offsets, it is important to investigate whether our method can handle various size of the retargeting image, especially when the image size is a fraction of the generators. In this case, conventional pixel based method \cite{Pritch09ICCV}\cite{He2012PO} often generates mis-stitched or mis-aligned objects: Figure \ref{fig:incompatible} a) and b) (top) are created using \cite{He2012PO}. In these examples objects are mis-aligned so they can be fit to the retargeted image. These artifacts can be better revealed in the building block label maps, as shown next to the retargeted images. In contrast, our method (bottom) is able to correct these artifacts using the same input offset labels. Specifically, in Figure \ref{fig:incompatible} a), our method consistently uses the ornament (green building block) to fill the middle of the facade; in Figure \ref{fig:incompatible} b), it snaps balcony and the lower floor window (yellow and blue building blocks). Since the same offset labels are used to create the results, these improvement purely comes from the building blocks constraints (Equation \ref{eq:EPixelSmooth}). Figure \ref{fig:incompatible} c) (top) is created using \cite{Pritch09ICCV} with a montange that is of the same size as the retargeted image. In this case the windows are distorted. Since we use a montage that is larger than the retarget image, regular structures are allowed to propagate beyond the image boundary. This is used to create Figure \ref{fig:incompatible} c) (bottom). Despite these successful examples, it is worth mentioning failure cases can occur for strongly incompatible image sizes. This will be discussed later in the paper with other failure cases.}

\begin{figure*}[t!]
  \centering
  \includegraphics[width=0.95\linewidth]{Fig/incompatible/incompatible}
  \caption{\revised{Our method is able to reduce artifacts when the synthesis image is of sizes that are incompatible to the offset labels. Top: result from \protect\cite{He2012PO} and \protect\cite{Pritch09ICCV}. Bottom row: our results.}} \label{fig:incompatible}
\end{figure*}

Figure \ref{fig:SynCompare} shows qualitative comparison between different synthesis methods. As readers can see blending based methods, such as \cite{Kwatra2005TO} and \cite{Simakov2008SV}, tend to create blur due to the averaging of conflicting image patches. Stitching based methods, such as \cite{Pritch09ICCV} and \cite{He2012PO}, do not create blur, but at the cost of creating visually implausible seams. Sometimes such seams are related to image semantic and is unavoidable if only pixel-level optimization is used. For example, in the facade example of Figure \ref{fig:SynCompare}, \cite{He2012PO} falsely stitched two different type of windows, as pointed out by the red arrow. In contrast, with building blocks constraint we are able to avoid such artefact based on a higher level of image understanding (see our supplementary video for more details).

>>>>

\markboth{xxx et al.}{Approximate \revised{Translational} Building Blocks for Image Parsing and Synthesis}

\title{Approximate \revised{Translational} Building Blocks for Image Parsing and Synthesis} % title

@@

\acmformat{xxx and xxx, 2015. Approximate \revised{Translational} Building Blocks for Image Parsing and Synthesis.  {ACM Trans. Graph.} xx, xx, Article xx (xx 2015), xx pages.\newline  DOI $=$
xxxx}

@@

\begin{abstract} 
In this paper, we introduce the concept of approximate \revised{translational} building blocks for fully-automatic image parsing. We consider translational repetitive elements in images and characterize building blocks as maximal, coherently transformed regions that are instantiated frequently. We develop an algorithm for constructing approximate building blocks from noisy and ambiguous image features, based on a spectral embedding of co-occurrence patterns. We evaluate our parsing method on a large benchmark data set and obtain clear improvements over state-of-the-art methods. \revised{We apply our image parsing method to texture synthesis, where we improve results by integrating building blocks constraints and building blocks offsets statistics into the conventional Markov Random Field models. We qualitatively evaluate our synthesis method on a number of benchmark data sets and obtain encouraging improvement over pixel based texture synthesis methods.}
\end{abstract}

@@

Our paper addresses the problem of finding \revised{translational} building blocks in image data using a fully unsupervised algorithm, i.e., it does not require any prior training data or user intervention. This restriction is very useful when we want to utilize the building block decompositions as structural side information for other tasks. We explore this exemplarily for image synthesis from example images.

@@

We replace structural priors by the assumption of coherently mapped building blocks, which are related by a common transformation and residual distortions. We discover such structures by relating co-occurance maps of images features using a spectral embedding, which draws its robustness out of the ability to use the whole \revised{4D (chris: this is in the old paper and I do not understand it now)} matching information in a single optimization for discovering coherently mapped pieces. We evaluate our method on a large benchmark data set of facade images. In comparison to previous methods, both with \cite{Wu2010DL} and without structural priors \cite{LIPMANsig2010,Liu2013GRASP}, we obtain a significant improvement.

To demonstrate the utility of building block information to generative tasks in computer graphics, we apply our method to guide image synthesis. Traditional texture synthesis methods~\cite{EfrosL99NP,Wei2000FT,Kwatra2003Graphcut,Kwatra2005TO} rely on a \revised{pixel based} Markovian structure model that is oblivious to higher level \revised{semantics} and therefore cannot produce images that are meaningfully structured on a coarser scale without human annotation~\cite{Hertzmann2001IA}. \revised{Our hypothesis is that as frequently occurring objects, building blocks can be used to guide image synthesis on a level higher than simple pixel comparisons. Specifically, preserving the shapes and the relative positions of the building blocks lead to better results. In this paper we explore labeling costs and offset statistics on the building blocks level and integrate them into a MRF model that can be optimized by graph cut. We show doing so indeed improves over pixel based approaches \cite{Kwatra2005TO}\cite{Simakov2008SV}\cite{Pritch09ICCV}. We also compare to the latest state-of-the-art method based on statistical priors of image offsets~\cite{He2012PO}. Our method yields comparable or better results, and provides an additional semantic annotation layer, which can used for user interaction in constrained image synthesis.}

In summary, the main contribution of this paper is a new approach for discovering \emph{approximate \revised{translational} building blocks} in unreliable data. We develop the idea in the context of an automatic image parsing technique that discovers translational building blocks, and outperforms previous methods in this task. We demonstrate the utility of the discovered building blocks and their geometric relations by applying it to image synthesis, where we can get improvements over unguided methods without sacrificing the fully automatic mode of operation.

@@

\textbf{Texture synthesis} has received a lot of attention in computer graphics, see \cite{Wei2009STAR} for a comprehensive survey. In order to overcome the limitations of the Markov Random Field (MRF) model, various forms of guidance have been employed, for example, using an additional image layer with user annotations \cite{Hertzmann2001IA} or on-the-fly user interaction ~\cite{Barnes2009,Hu2013PPI}. Automating the creation of guidance map is still an on-going research topics, with some success in low level feature maps. For example, Lefebvre and Hoppe~\shortcite{Lefebvre2006ATS} use distance transforms on feature maps to guide the synthesis of high-quality textures with pronounced meso-structure. However, the feature transform cannot structure complex images beyond textures. Rosenberger et al.~\shortcite{Rosenberger2009LSS} extend the idea to irregular textures with non-stationary statistics, such as aged or weathered surfaces. Dishler et al.~\shortcite{Dischler2002} use ``texture particles'' as landmarks, similar to our guidance scheme; however, only textures (with some meso-structure) are synthesized due to limitations in the detection stage. Tiling grammars have been recently employed to guide the placement of discrete elements~\cite{Ma2011DET,Ma2013DET}, however our method handles image data, such as pixels color and class labels, rather than discrete elements. Our application is also related to image retargeting, recomposition and inpainting. Along this direction, various methods have been experimented to avoid local optimal solutions results from the MRFs model. For example, \cite{Simakov2008SV} uses bidirectional matching and a gradual resizing procedure for retain the image structure in retargeting (especially for image shrinking); \cite{Pritch09ICCV,He2012PO} studied pixel offset, and use graph cut to find the optimal pixel assignment for the output image that produces a smooth offset field. Nonetheless, these methods all operate on image pixels, hence can not eliminate structural artefacts. An exception is \cite{Wu2010SS}, which use deformable lattice to retain structure during image resizing. However their method is restricted to images has a global repetition (such as lattice), and is difficult to be used for recomposition. In this paper we will show using additional \revised{building blocks} knowledge is able to improve the performance of the conventional pixel based MRF methods.

@@

\subsection{Dataset}
In order to prove our algorithm is able to identify meaningful building blocks, we conduct an evaluation on the fa{\c{c}}ade data set created by \cite{ZHANGsig13}. This data set contains 600 fa{\c{c}}ade images of various structures. For each image a box pattern has been interactive created by the authors, identifying repetitive elements such as windows or balconies. We use these labels as the ground truth to quantitatively evaluate our detection. We remove non-repetitive boxes from the data set (7285 boxes remain). We also test our algorithm on a collection of non-facade images. The results are briefly discussed at the end of this section.

@@

\revised{
\subsection{Non-facade images}
We also collect our own data set, consisting of images from Flickr and the datast used in \cite{Liu2013GRASP},  with focus on irregular, approximately translational repetitions and more challenging correspondence problems. Figure \ref{fig:NonFacade} shows some examples. As expected, the grid based methods fails on most of these cases (returning only a grid for the first image in the second row), while the more general building block model still performs well. However, our current implementation is restricted to translational building blocks. As the consequence it does not handle more complex scenes with strong perspective and rotational symmetries. }

\begin{figure*}[t]
  \centering
  \includegraphics[width=1\linewidth]{Fig/NonFacade/NonFacade}
  \caption{\revised{Detection on non-fa{\c{c}}ades images.}} \vspace{-10pt}\label{fig:NonFacade}
\end{figure*}

@@

\revised{
The key idea is to augment the conventional pixel based MRF models \cite{Pritch09ICCV} using an additional layer of building block information. We propose two different types of building blocks \revised{information}: first, each pixel has a building block class label (zero for the background), so it should be distinguishable from pixels of different classes. Second, each pixel, except for the background, can be augmented by the local coordinate frame of its parent building block, so it can be distinguished from other pixels inside the same building block. Inspired by the success of pixel offset statistics \cite{He2012PO}, we also use building blocks offset statistics to generate better candidate shifts for stitching.}

\revised{
The rest of this section explains how to apply building blocks for two specific applications: image targeting and interactive editing. Although in this paper we design our synthesis methods based on image stitching (\cite{Pritch09ICCV,He2012PO}), in principle building blocks can be also applied to synthesis methods that use patch blending, such as \cite{Kwatra2005TO} and \cite{Simakov2008SV}. We choose to focus on the former methods because they perform better for synthesizing regular or semi-regular structures. Nonetheless results from \cite{Kwatra2005TO} and \cite{Simakov2008SV} will also be compared in the paper and in the supplementary materials.}

@@

The goal of image retargeting is to synthesis new images by resizing. In \cite{Pritch09ICCV} and \cite{He2012PO} this is cast as a labeling problem, where each pixel in the synthesized image is assigned with a offset label that maps it back to the input image. Candidate labels $L$ can be generated by prescription \cite{Pritch09ICCV},  or by co-occurrence statistics \cite{He2012PO}. They are assigned to the synthesized image by minimizing the standard MRF energy function (Equation \ref{eq:GC}). Although these method are designed to find optimal labeling assignment, implausible stitches can still occur due to only pixel level energy is minimized (Figure \ref{fig:IntermediumSyn}, b)). \revised{To overcome this problem, we incorporate building block constraints and building block offsets statistics as described in rest of this section. }

\subsubsection{\revised{Building Blocks Constraints}}

\revised{The idea is straight forward: as frequently appearing objects, building blocks should be prevented from being mis-configured and distorted.} Based on this idea, we define the smoothness term as the following:

\revised{
\begin{equation}
E_{s} = \omega_{1}E_{s}^{pixel} + \omega_{2}E_{s}^{class} + \omega_{3}E_{s}^{position}
\label{eq:ESmooth}
\end{equation}
}

Here $E_{s}^{pixel}$ is the conventional pixel-based smoothness term as used by \cite{Pritch09ICCV} and \cite{He2012PO}. It penalizes two neighboring labels $a, b$ that creates a seam for adjacent pixels $x, x'$:
%
\begin{equation}
E_{s}^{pixel}(x, x', a, b) = |I(x + s_{a}) - I(x + s_{b})| + |I(x' + s_{a}) - I(x' + s_{b})|
\label{eq:EPixelSmooth}
\end{equation}
%
In addition to it, we introduce two new constraints: the class smoothness cost $E_{s}^{class}$ and the position smoothness cost $E_{s}^{position}$. They are Potts models with different building blocks properties.

\revised{\textbf{Class smoothness costs} penalizes labeling that leads to topologically mis-configured building blocks. Let $l(x)$ be the building blocks class label for pixel $x$, the class smoothness term computes the hamming distance between class labels for two adjacent pixels $x, x'$:}

\begin{equation}
\revised{
E_{s}^{class} = l(x + s_{a}) \neq l(x + s_{b}) + l(x' + s_{a}) \neq l(x' + s_{b})}
\label{eq:class}
\end{equation}

\revised{It checks the tilings of different building blocks, and penalizes the ones that are not observed in the input image. In this way the topology of building blocks is preserved in the retargeted image.}

%It penalizes falsely stitching together pixels from different building block classes. \revised{This is very important for reducing topological mis-configuration that tiles different classes of building blocks in any unobserved fashion.}

\revised{\textbf{Position smoothness costs} penalizes labeling that leads to local deformed building blocks. Let $(r(x), c(x))$ be the relative row and column positions for pixel $x$ in its parent building blocks's local frame. The position smoothness cost computes a weighted sum of Manhattan distances:}

\footnotesize
\begin{equation}
\begin{split}
\revised{E_{s}^{position} = w(x)(|r(x + s_{a}) - r(x + s_{b})| + |c(x + s_{a}) - c(x + s_{b})|)} \\
\revised{+ w(x')(|r(x' + s_{a}) - r(x' + s_{b})| + |c(x' + s_{a}) - c(x' + s_{b})|)}
\end{split}
\label{eq:position}
\end{equation}
\normalsize

\revised{It differentiates internal pixels of a building block and penalizes any local deformation that leads to mis-aligned or distorted building blocks. Notice $r(x)$ and $c(x)$ are normalized according to the size of the parent building block: $r(x) \in [0, 1]$ and $c(x) \in [0, 1]$. This allows us to control the upper bound of this cost}. \revised{In the meantime, $w(x)$ is a switch that only turns on for a smooth class labeling:}

\begin{equation*}
\revised{
w(x) = \left\{
\begin{array}{rl}
1 & \text{if } l(x + s_{a}) == l(x + s_{b}),\\
0 & \text{otherwise} 
\end{array} \right.
}
\end{equation*}

%\begin{equation}
 %\revised{$w(x) = l(x + s_{a}) == l(x + s_{b})$} 
%\end{equation}

\revised{This means local deformation is only tested for a topologically correct labeling. Any unsmooth class labeling will not be penalized again here.}

%In the mean time this cost is only activated for pixels that are assigned with the same class label, \revised{that is, $w(x) = l(x + s_{a}) == l(x + s_{b})$. This is because labeling that leads to $l(x + s_{a}) \neq l(x + s_{b})$ is guaranteed to be penalized by the class smoothness cost and should not be penalized again here.}

@@

 \revised{\textbf{Weights:} Notice the three costs in Equation \ref{eq:ESmooth} share the same lower bound (zero) but different upper bounds: $sup E_{s}^{pixel} = 255 \times 2 = 500$, $sup E_{s}^{class} = 1 \times 2 = 2$, and $sup E_{s}^{position} = 1 \times 4 = 4$. This implies we should weight them carefully so none of them, especially $E_{s}^{pixel}$, becomes predominant. In practice we also observed that artifacts in the conventional MRF models are rarely created by large $E_{s}^{pixel}$, as large pixel costs are naturally removed by graph cut as obvious seams. In fact, the challenging artifacts are often caused by pixels of similar values, in which case $E_{s}^{pixel}$ is small. This leads to the conclusion that $E_{s}^{class}$ and $E_{s}^{position}$ should be weighted to reduce artifacts co-occurring with low $E_{s}^{pixel}$, instead of its theoretical upper bound. In practice we find $\omega_{1} = 1, \omega_{2} = 10, \omega_{3} = 2$ works robustly across a wide range of images. Although they can be further tuned on a per image basis for better results, we fix them to these default values in the later evaluation for fair comparisons.}

\revised{Figure \ref{fig:IntermediumSyn} shows an example of how the building blocks constraints improve the result. The conventional MRF based method \cite{Pritch09ICCV} creates the result in Figure \ref{fig:IntermediumSyn} b). While the stitching of the arches is clearly artificial to human, it is hard to be avoided if only pixel cost is considered. With the help of the additional building blocks costs we are able to reduce the artifacts, as shown in Figure \ref{fig:IntermediumSyn} c). The improvement is more obvious in the class label maps, shown in the bottom row. Especially, the noisy yellow labels at the bottom of b) is removed from c). This leads to a better configuration of the arches.}

\subsubsection{\revised{Building Blocks Offset Statistics}}
\revised{Another important factor for achieving high quality synthesis is the input offset labels for graph cut optimization. These labels directly decide the complexity of the search space and whether the minimized energy leads to a visually plausible image. For example, regularly sampling offset labels is not optimal for image completion, as observed by \cite{He2012PO}. This is also true for image regarting. For example, in Figure \ref{fig:IntermediumSyn} c) a window is squeezed at the center of the image, despite the use of building blocks constraints. This is due to the fact that offset labels are sampled using a grid generator that deviates from regularities in the facade. In summary, building blocks constraints are less useful if the search space does not accommodate a useful solution in the first place.}

\revised{To address this problem, we sample offset labels from statistics of building blocks. In this way both the search space is constructed based on the regularity in the image. This often leads to further improvement of the synthesis results, as shown in Figure \ref{fig:IntermediumSyn} d). Our sampling contains two main steps: It first computes predominant offsets between the same class of building blocks. These offsets are then used as generators to regularly generate input labels for graph cut. Specifically, it works as follows: A probability density map (PDF) is computed by accumulating votes of pairwise building blocks offsets. Only building blocks of the same class are considered in the voting. We then detect local peaks in the PDF using non-maximum suppression. These local peaks were used in previous works as offset labels for image completion, as described in \cite{He2012PO}. Differently, for our task of image retargeting a larger montage must be created to cover the synthesis domain. In theory this can be achieved by recursively sampling new peaks from the PDF. However the number of offsets will be increased by a power function and the search becomes infeasible in practice. To handle this problem, we find predominant offsets and use them as grid generators to efficiently create the montage: the first generator is the strongest peak in the PDF, and the second generator is the next strongest peak that satisfies a minimum angular distance to the first generator. The minimum angular (set to $\frac{\pi}{3}$) requirement de-correlates the two generators so the montage can be efficiently expanded as a 2-D grid. In the pursuit of higher variability in the results, additional generators can be combined with these two to create extra grids. For example, randomness in the synthesis results can be created using a near-regular grid. However, in practice we found a regular grid spanned by two predominate generators trades off well between stability and variability.}

\revised{Since we use grid based offsets, it is important to investigate whether our method can handle various size of the retargeting image, especially when the image size is a fraction of the generators. In this case, conventional pixel based method \cite{He2012PO} often generates mis-stitched or mis-aligned objects: Figure \ref{fig:incompatible} a) and b) (top) are created using \cite{He2012PO}. In these examples objects are mis-aligned so they can be fit to the retargeted image. These artifacts can be better revealed in the building block label maps, as shown next to the retargeted images. In contrast, our method (bottom) is able to correct these artifacts using the same input offset labels. Specifically, in Figure \ref{fig:incompatible} a), our method consistently uses the ornament (green building block) to fill the middle of the facade; in Figure \ref{fig:incompatible} b), it snaps balcony and the lower floor window (yellow and blue building blocks). Since the same offset labels are used to create the results, these improvement purely comes from the additional building blocks constraints in Equation \ref{eq:EPixelSmooth}. Figure \ref{fig:incompatible} c) (top) is a more challenging example with strongly incompatible image size. In this case, even our method produces artifacts. However, this can be easily resolved by using a montage that is larger than the retarget image, so the regular structure can propagate beyond the image boundary. This is used to create Figure \ref{fig:incompatible} c) (bottom). Despite these successful examples, it is worth mentioning that failure cases can occur for strongly incompatible image sizes. This will be discussed later in the paper with other failure cases.}

\begin{figure*}[t!]
  \centering
  \includegraphics[width=0.95\linewidth]{Fig/incompatible/incompatible}
  \caption{\revised{Our method is able to reduce artifacts when the synthesis image is of sizes that are incompatible to the offset labels. Top a) and b): result from \protect\cite{He2012PO}. Bottom a) and c): our results generated with \protect\cite{He2012PO}'s offset labels. Top c): our result with an montage that is of the same size of the retarget image. Top d): our result with an montage that is larger than the retarget image.}} \label{fig:incompatible}
\end{figure*}
